### 2022-06-29 manuscript/manuscript.Rmd
clarify use of ultra-high resolution

In the last decade, there has been a proliferation in the use of high resolution (HR) MS instrumentation with Orbitrap mass analysers becoming the standard for HRMS.
These mass analysers have provided extraordinary increases in attainable mass resolution, precision and accuracy.
But this has also created new challenges for the post-acquisition spectral processing of mass spectra obtained from these instruments with magnitude increases in the volumes of data that can be acquired per sample.

>>>>

In the last decade, there has been a proliferation in the use of ultra-high resolution (HR) MS instrumentation with Orbitrap mass analysers becoming the standard for HRMS.
These mass analysers have provided extraordinary increases in attainable mass resolution, precision and accuracy.
But this has also created new challenges for the post-acquisition spectral processing of mass spectra obtained from these instruments with magnitude increases in the volumes of data that can be acquired per sample.
